\documentclass[12 pt]{article}

\usepackage{stoversymb}
\usepackage{fullpage,amsmath,amsfonts,amssymb,url,multicol}
%===makes urls render well===
\usepackage{lmodern}
\usepackage[T1]{fontenc}
%============================
\usepackage{wasysym} % smileys
\usepackage[inline]{enumitem}

%,amsthm,amscd,amsbsy,graphpap,makeidx,xfrac,graphicx,floatflt,verbatim,tikz}

%\usetikzlibrary{matrix,arrows}

\everymath{\displaystyle}

\setenumerate{itemsep=0.25in}
\setlist[enumerate,1]{label=\arabic*.}
\setlist[enumerate,2]{label={(\alph*)}}
\setlist[enumerate,3]{label={\roman*.}}

\newcommand{\hint}[1]{\hspace{0.5in}\textbf{Hint}: #1}

\begin{document}
\begin{flushright}Name: \line(1,0){200}\end{flushright}
\begin{center}
\Large{\textbf{MAC 2312 --- Homework 1}}
\end{center}
\textbf{Directions:} Complete the following problems (front and back) for a homework grade. Answers given without showing work will not be eligible to receive partial credit. Problems \textit{must} be neatly written up and presented in a professional manner in order to receive credit. \textbf{Date Due:} \textit{Either} September 15, 2016 \textit{or} September 20, 2016.
\vspace{0.125in}
\begin{enumerate}[leftmargin=0in, rightmargin=-0.25in]
	%========Slack==============
	\item \begin{enumerate}
		\item Navigate to our course homepage at
		\begin{center} \url{http://www.math.fsu.edu/~cstover/teaching/fa16_2312/}
		\end{center}
		\item Read and familiarize yourself with the three resources listed under \textit{Supplementary Resources} on the \textsc{General Info} tab.
		\item Follow the instructions for using \textsc{Slack} messenger.\begin{quote}\textbf{Note:} This may require that I approve your email address, so to avoid some last minute glitch where I don't get to your approval on-time, please don't wait to do this!\end{quote}
		\item Navigate to the channel \url{#three_things_about_me} in the left column under \textsc{Channels} (its browser url should be something like \url{https://fall2016-calc2.slack.com/messages/three_things_about_me/}) and post three random things about yourself.\begin{quote}\textbf{Note:} This will be visible to everyone who signs into our class's chat room, so you definitely want to keep this PG-13, safe for work, and non-incriminatory. {\Large\smiley}\end{quote}
	\end{enumerate}
	%========u-sub, etc.==============
	\item Compute each of the following integrals, noting that each can be found using ``old knowledge'' (i.e., techniques you knew before learning IBP).\begin{enumerate}
		\item $\int\tan(x)\,dx$
		\vspace{0.25in}
		\item $\int\sec(x)\,dx$\hint{$\frac{\sec(x)+\tan(x)}{\sec(x)+\tan(x)}=1$.}
	\end{enumerate}
	\newpage
	%========IBP==============
	\item \begin{enumerate}
		\item Use the product rule for derivatives to derive the identity for integration by parts:
		$$\int f(x)g'(x)\,dx=f(x)g(x)-\int f'(x)g(x)\,dx.$$
		\item Evaluate each of the following using integration by parts.
		\begin{enumerate}
			\item $\int (2x+2)e^{-x}\,dx$
			\item $\int_{\sqrt{\pi}}^{\pi^2}(x^2+2x+1)e^{-x}\,dx$
			\item $\int x^3\sqrt{1+x^2}\,dx$\hint{If you try to integrate $\sqrt{1+x^2}$, you'll have a bad day.}
			\item $\int\arcsin(3x)\,dx$
			\item $\int 2x\arctan(x)\,dx$\hint{$\frac{a^2}{1+a^2}=\frac{(1+a^2)-1}{1+a^2}$}
			\item $\int (\arcsin(x))^2\,dx$
			\item $\int x\tan^2(x)\,dx$\hint{$\tan^2(x)=\sec^2(x)-1$.}
		\end{enumerate}
		\vspace{0.25in}
		\red{\item Use the method of cylindrical shells to find the volume generated by rotating the region bounded by the curves $y=\cos(\pi x/2)$, $y=0$, $x=0$, and $x=1$ about the $y$-axis.\vspace{0.25in}
		\item
		\begin{enumerate}
			\item Use integration by parts to prove that $\int f(x)\,dx=xf(x)-\int xf'(x)\,dx.$
			\vspace{0.25in}
			\item Using the above formula along with the definition $\operatorname{LI}(x)\deff \int \frac{1}{\ln(x)}\,dx$, calculate\vspace{-0.125in}
			$$\int \ln(\ln(x))\,dx.$$
		\end{enumerate}}
	\end{enumerate}
	\newpage
	%========trig integrals==============
	\item \begin{enumerate}
		\item Compute each of the following trig integrals.
		\begin{enumerate}
			\item $\int \sec^2(\theta) \tan^3(\tan(\theta))\,d\theta$\hint{Let $u=\tan(\theta)$; then, see Example 7 in \S 7.2.}
			\item $\int \sin^5(\phi)\cos^3(\phi)\,d\phi$
			\item $\int \sin(5x)\cos(8x)\,dx$
			\item $\int \sin^2(x)\cos^8(x)\,dx$
		\end{enumerate}
		\vspace{0.25in}
		\item Evaluate 
		$$\int\sin(x)\cos(x)\,dx$$
		by four methods: \begin{enumerate*}[label=(\roman*)]\item the substitution $u=\cos(x)$; \item the substitution $u=\sin(x)$; \item the identity $\sin(2x)=2\sin(x)\cos(x)$; and \item integration by parts.\end{enumerate*}\vspace{0.5in}
		\item Find the average value of the function $f(x)=\sin^2(x)\cos^2(x)$ on the interval $[-\pi, 32\arctan(19)]$.\vspace{0.5in}
		\red{\item Assuming $m$ and $n$ are positive integers (i.e., $m,n\in\PositiveIntegers$), prove each of the following identities:\vspace{0.125in}
		\begin{enumerate}
			\item $\int_{-\pi}^{\pi}\sin(mx)\cos(nx)\,dx=0$
			\item $\int_{-\pi}^{\pi}\sin(mx)\sin(nx)\,dx=\left\{\begin{array}{lcr}0 & \text{if} & m\neq n \\ \pi & \text{if} & m = n\end{array}\right.$\item $\int_{-\pi}^{\pi}\cos(mx)\cos(nx)\,dx=\left\{\begin{array}{lcr}0 & \text{if} & m\neq n \\ \pi & \text{if} & m = n\end{array}\right.$
		\end{enumerate}}
	\end{enumerate}
	\newpage
	%========trig sub==============
	\item \begin{enumerate}
		\item Evaluate each of the following integrals.
		\begin{enumerate}
			\item $\int\frac{x^3}{\sqrt{x^2+4}}\,dx$
			\item $\int\sqrt{4-x^2}\,dx$
			\item $\int\frac{dt}{t^5\sqrt{9t^2-16}}$
			\item $\int\frac{y^2}{(3+4y-4y^2)\sqrt{3+4y-4y^2}}\,dy$
			\item $\int\frac{k^2}{(k^2+a^2)^{3/2}}\,dk$
		\end{enumerate}\vspace{0.125in}
		\item Find the area of the region bounded by the hyperbola $16x^2-9y^2=144$ and the line $x=3\sqrt{2}$.\vspace{0.25in}
		\item Compute each of the following integrals using both of the methods stated.
		\begin{enumerate}
			\item $\int\frac{x^3}{(9-x^2)^{5/2}}\,dx$ using
			
			\hspace{0.5in}\begin{enumerate*}[label=(\arabic*)]\item the substitution~$x=3\sin(\theta)$, and \item \red{the substitution~$u^2=9-x^2$.}\end{enumerate*}\vspace{0.375in}
			
			\item $\int\frac{1}{x^4(9+x^2)^{1/2}}\,dx$ using
			
			\hspace{0.5in}\begin{enumerate*}[label=(\arabic*)]\item the substitution~$x=3\tan(\theta)$, and \item \red{the substitution~$u^2=\frac{9+x^2}{x^2}$.}\end{enumerate*}\vspace{0.375in}
			
			\item $\int\frac{1}{x\sqrt{x^2-1}}\,dx$ using
			
			\hspace{0.5in}\begin{enumerate*}[label=(\arabic*)]\item the substitution~$x=\sec(\theta)$, and \item \red{the substitution~$u^2=x^2-1$.}\end{enumerate*}
		\end{enumerate}
	\end{enumerate}
	\newpage
	%========partial frac==============
	\item \begin{enumerate}
		\item Write out the form of the partial fraction decomposition of the following functions but \textit{do not} determine the numerical values of the coefficients (see Example 7 in \S 7.4).
		\begin{enumerate}
			\item $\frac{t^6+1}{t^6+t^3}$
			\item $\frac{x^5+x^3+1}{(x^2-x)(x^4+2x^2+1)}$
		\end{enumerate}
		\item Evaluate each of the following integrals.
		\begin{enumerate}
			\item $\int\frac{10}{(y-1)(y^2+9)}\,dy$
			\item $\int\frac{x^3+2x^2+3x-2}{(x^2+2x+2)^2}\,dx$
			\item $\int\frac{8+x}{3x^3+13x^2+18x+8}\,dx$\hint{$x=-1$ is a root of the denominator.}
			\item $\int\frac{2+v^4}{v^3+9v}\,dv$
			\item $\int\frac{e^{2z}}{e^{2z}+3e^z+2}\,dz$
		\end{enumerate}
		\red{\item\begin{enumerate}
			\item If $t=\tan(x/2)$, sketch a right triangle to prove that
			$$\cos\left(\frac{x}{2}\right)=\frac{1}{\sqrt{1+t^2}}\hspace{0.5in}\text{and}\hspace{0.5in}\sin\left(\frac{x}{2}\right)=\frac{t}{\sqrt{1+t^2}}.$$
			\item Show that $\cos(x)=\frac{1-t^2}{1+t^2}$, $\sin(x)=\frac{2t}{\sqrt{1+t^2}}$, and $dx=\frac{2}{1+t^2}\,dt$.\vspace{0.25in}
			\item Use the above substitutions to evaluate
			$$\int_{\pi/3}^{\pi/2}\frac{1}{1+\sin(x)-\cos(x)}\,dx$$
			by transforming the integrand into a rational function of $t$.
		\end{enumerate}}
	\end{enumerate}
	\newpage
	%========techniques==============
	\item Solve each of the following integrals using any of the methods you know.
	\begin{multicols}{2}
		\begin{enumerate}
			\setlength{\itemsep}{0.625in}
			\item $\int(4y+2)^{\sqrt{\pi}}\,dy$
			\item $\int t\sin(t)\cos(t)\,dt$
			\item $\int_0^4\frac{x-1}{x^2-4x-5}\,dx$
			\item $\int e^{x+e^x}\,dx$
			\item $\int\frac{\ln(x)}{x\,(1+(\ln(x))^2)^{3/2}}\,dx$
			\item $\int\left(\ln(x)+\frac{3x^2-2}{x^3-2x-8}\right)\,dx$
			\item $\int\sin\left(\sqrt{t \sqrt{2}}\right)\,dt$
			\item $\int\frac{\sec(\theta)\tan(\theta)}{\sec^2(\theta)-\sec(\theta)}\,d\theta$
			\item $\int\theta\tan^2(\theta)\,d\theta$
			\item $\int_0^1 x\sqrt{2-\sqrt{1-x^2}}\,dx$
			\item $\int\frac{dx}{x\sqrt{4x^2-1}}$
			\item $\int\cos(x)\cos^3(\sin(x))\,dx$
			\item $\int_{\pi/4}^{\pi/3}\frac{\ln(\tan(x))}{\sin(x)\cos(x)}\,dx$
			\item $\int\frac{dx}{\sqrt{x}(2+\sqrt{x})^4}$
			\item $\int\frac{1}{(x-2)(x^2+4)}\,dx$
			\item $\int\frac{dy}{\sqrt{4y^2-4y-3}}$
		\end{enumerate}
	\end{multicols}
\end{enumerate}
\end{document}