\documentclass[12 pt]{article}

\input{../hwHeader}

\begin{document}
\begin{flushright}Name: \line(1,0){200}\end{flushright}
\begin{center}
\Large{\textbf{MAS 3105 --- Homework 3}}
\end{center}
\textbf{Directions:} Complete the following problems for a homework grade, being sure to adhere to the \ul{Homework Policy} on the \ul{Homework} tab of the course webpage
\begin{center}
	 \url{http://www.math.fsu.edu/~cstover/teaching/sp18_mas3105/}.
\end{center}
\textbf{Date Due:} Tuesday, April 3.
\vspace{0.125in}
\begin{enumerate}[leftmargin=0in, rightmargin=-0.25in]
%	%========Slack==============
	\item Go to the \textbf{\#hw3} channel in our course's \textsc{Slack} room (see course homepage for the URL) and 
	\begin{enumerate}[label=(\roman*),itemsep=0mm] 
		\item post $\geq 1$ thing about this homework; and 
		\item reply to $\geq 1$ of your classmates' posts.
	\end{enumerate}
	
	\note{Yes, you will get graded for this question. \smiley}
	
	\vspace{-0.375in}
	
	\item For each of the following matrices $\sansA$,
	\begin{enumerate}[label=(\roman*),leftmargin=16mm,itemsep=2.5mm]
		\item put $\sansA$ into $\RREF$;
		\item find a basis for $\col(\sansA)$;
		\item compute $\dim(\col(\sansA))$;
		\item find a basis for $\row(\sansA)$;
		\item compute $\dim(\row(\sansA))$;
		\item find a basis for $\nul(\sansA)$;
		\item compute $\dim(\nul(\sansA))$; and
		\item verify the rank-nullity theorem for $\sansA$.
	\end{enumerate}
	
	\vspace{3mm}

	\begin{adjustwidth}{-0.125in}{-0.125in}
		\begin{multicols}{3}
			\begin{enumerate}[itemsep=6mm]
				\item $\sansA=\pmat{1 & -1 & 1 & 3 \\ 0 & 2 & 3 & 1 \\ 3 & -7 & -3 &  7}$
				\item $\sansA=\pmat{-2 & 1 & 3 \\ 4 & 1 & 1 \\ 1 & 0 & 1 \\ 0 & 2 & 2 \\ 3 & -2 & 4}$
				\item $\sansA=\pmat{1 & 2 & 3 & 4 \\ 5 & 6 & 7 & 8 \\ -1 & -2 & 3 & -4 \\ 9 & 10 & -11 & 12}$
			\end{enumerate}
		\end{multicols}
	\end{adjustwidth} 

	\vspace{-12mm}
	
	\item For each of the matrices $\sansA$ in Problem 2, repeat parts (i)--(viii) (of problem 2) for the matrix $\sansA^\sansT$.
	
	\newpage
	
	\item For each of the following linear transformations $\rmTT$,
	\begin{enumerate}[label=(\roman*),leftmargin=16mm,itemsep=2.5mm]
		\item find the domain and codomain of $\rmTT$;
		\item find the canonical matrix $\sansA$ for $\rmTT$;
		\item find $\range(\rmTT)$;
		\item find the dimension of $\range(\rmTT)$;
		\item find $\ker(\rmTT)$; and
		\item find the dimension of $\ker(\rmTT)$;
	\end{enumerate}
	Assume that $x_1$, $x_2$, $x_3$, and $x_4$ are all real numbers.
	
	\vspace{3mm}
	
	\begin{enumerate}[itemsep=12mm]
		\item $\rmTT:\pmat{x_1 \\ x_2}\MapsTo\pmat{x_1 \\ x_1 - x_2 \\ x_2 \\ x_2 - x_1 \\ 2x_1+3x_2}$
		\item $\rmTT:\pmat{x_1 \\ x_2 \\ x_3 \\ x_4}\MapsTo\pmat{x_1-x_4 \\ x_2-x_3}$
		\item $\rmTT:\pmat{x_1 \\ x_2 \\ x_3 \\ x_4}\MapsTo\pmat{x_4 \\ -x_1 \\ x_2-x_3-x_4 \\ x_1-x_2-x_3}$
	\end{enumerate}

	\item For each of the linear transformations in Problem 4, repeat parts (i)--(vi) (of problem 4) for the linear transformation $S(\vect{x})=\sansA^\sansT\vect{x}$ (where $\sansA$ is the canonical matrix of the transformation in question).
	
	\newpage
	
	\item Let $\sansA=\left(
	\begin{array}{ccccccc}
	7 & -9 & -4 & 5 & 3 & -3 & -7 \\
	-4 & 6 & 7 & -2 & -6 & -5 & 5 \\
	5 & -7 & -6 & 5 & -6 & 2 & 8 \\
	-3 & 5 & 8 & -1 & -7 & -4 & 8 \\
	6 & -8 & -5 & 4 & 4 & 9 & 3 \\
	\end{array}
	\right)$.
	\begin{enumerate}[itemsep=20mm,topsep=6mm]
		\item Construct a matrix $\sansC$ whose columns are a basis for $\col(\sansA)$.
		\item Construct a matrix $\sansN$ whose columns are a basis for $\nul(\sansA)$.
		\item Construct a matrix $\sansR$ whose rows are a basis for $\row(\sansA)$.
		\item Construct a matrix $\sansM$ whose columns are a basis for $\nul(\sansA^\sansT)$.
		\item Form the augmented matrix $\sansS=\pmatgrid{c|c}{\sansR^\sansT & \sansN}$. What are its dimensions?
		\item Find the determinant for $\sansS$ and the inverse $\sansS^{-1}$, if they exist. If not, state why.
		\item Form the augmented matrix $\sansT=\pmatgrid{c|c}{\sansC & \sansM}$. What are its dimensions?
		\item Find the determinant for $\sansT$ and the inverse $\sansT^{-1}$, if they exist. If not, state why.
	\end{enumerate}
\end{enumerate}
\end{document}